Equalizer\\Programming and User Guide

### 2010-02-22 Developer/ProgrammingGuide/paper.tex
Programming Guide: update slave object commit section Doxygen warning fixes
[ ] May break build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\fig{fSlaveCommit} depicts one possible communication sequence. In general, it
is best to adhere to the following rules:
\begin{itemize}
\item Handle the case that a slave instance will receive its own changes again.
\item Write your application code so that only one object instance is modified
  at any given time. 
\item When multiple slave instances have to modify the same object at the same
  time, try to modify and serialize disjunct data of the object.
\item Before modifying a slave instance, \textsf{sync} it to the head version.
\item Write serialization code defensively, e.g.:
  \begin{itemize}
  \item When adding a new child to an object, check that it has not been added
    already.
    \item When removing a child, transmit the child's identifier instead of its
      index for removal.
    \item Modify a variable by serializing its value (instead of an operation on
      it) so that the last change will win.
  \end{itemize}
\end{itemize}

@@

Multiple instances of the same object (identifier) can be mapped on the
same node and session simultaneously. Each object instance has a
node-unique instance identifier. When the instance ID is set to
\textsf{EQ\_ID\_ANY} (the default value), a command is dispatch to all
object instances registered to the session with the correct object
ID. Multiple object instance per node are used when different threads on
the node need to process a different version of the same object.

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netObject.pdf}
  {\caption{\label{fNetObject}Communication between two Objects}}
\end{wrapfigure}
Distributed objects provide data synchronization functionality, as described
above. Additionally, applications can send command packets by creating custom
object packets with a command greater than \textsf{CMD\_OBJECT\_CUSTOM}.

>>>>

\fig{fSlaveCommit} depicts one possible communication sequence. In general, it
is best to adhere to the following rules:
\begin{itemize}
\item Handle the case that a slave instance will receive its own changes again.
\item Set the appropriate dirty bits when unpacking slave delta data on the
  master object instance.
\item Write your application code so that only one object instance is modified
  at any given time. 
\item When multiple slave instances have to modify the same object at the same
  time, try to modify and serialize disjunct data of the object.
\item Before modifying a slave instance, \textsf{sync} it to the head version.
\item Write serialization code defensively, e.g.:
  \begin{itemize}
  \item When adding a new child to an object, check that it has not been added
    already.
    \item When removing a child, transmit the child's identifier instead of its
      index for removal.
    \item Modify a variable by serializing its value (instead of an operation on
      it) so that the last change will win.
  \end{itemize}
\end{itemize}

@@

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netObject.pdf}
  {\caption{\label{fNetObject}Communication between two Objects}}
\end{wrapfigure}
Multiple instances of the same object (identifier) can be mapped on the
same node and session simultaneously. Each object instance has a
node-unique instance identifier. When the instance ID is set to
\textsf{EQ\_ID\_ANY} (the default value), a command is dispatch to all
object instances registered to the session with the correct object
ID. Multiple object instance per node are used when different threads on
the node need to process a different version of the same object.

Distributed objects provide data synchronization functionality, as described
above. Additionally, applications can send command packets by creating custom
object packets with a command greater than \textsf{CMD\_OBJECT\_CUSTOM}.
